---
title: 'W241 Project - MASA'
author: Adam, Alla, Grant, and Siobhan
output:
  pdf_document: default
  html_document: default
urlcolor: blue
---

```{r}
# load packages 
library(foreign)
library(data.table)
library(foreign)
library(dplyr)
library(tidyr)
library(data.table)
library(magrittr) 
library(lmtest)
library(sandwich)
library(stargazer)
library(multiwayvcov)
library(ggplot2)
#library(hmisc)

#install.packages('Hmisc')
```

First we read in the data.  The two csv files represent respondents from the groups social media and Fulcrum respondents respectively.

```{r}
d1 <- read.csv("./Data/Enrollment-With Learnings.csv", header = T)
d2 <- read.csv("./Data/Enrollment-With Learnings-for Fulcrum.csv", header = T)
#immediately remove email addresses
d1$Q26 <-NULL
d1 <- d1[-c(1,2) ,]
d2 <- d2[-c(1,2) ,]

#Add Source Column to tell if data came from Fulcrum or other source
d1$Fulcrum = 0
d2$Fulcrum = 1

alldata <- rbind(d2, d1)
head(alldata,3)
```

```{r}
get.confidence <- function(estimate,error) {
  lower_bound = estimate - 1.96*error
  upper_bound = estimate + 1.96*error
  interval = c(lower_bound, upper_bound)
  return(interval)
}
```

Next, we remove some personally identifying information, and other info we wont use as part of the anlysis.  

```{r}
#Remove Stuff
drop <- c("RecipientFirstName","RecipientLastName","RecipientEmail","ExternalReference","rid","zip")
```

Next we split the date into columns for month data and year.  This will be used to remove responses from initial testing

```{r}
#Remove Test Records NEEDS UPDATING AS WE HAVE MORE DATES AVAILABLE NOW
alldata = separate(alldata,StartDate,c("StartDate","StartTime"), sep=" " ,remove = TRUE)
alldata = separate(alldata,StartDate,c("StartMonth","StartDay","StartYear"), sep="/" ,remove = TRUE)
```

Next we remove responses from initial testing, as well as non US citizens or residents

```{r}
alldata = alldata[as.numeric(alldata$StartDay) >= 13,]

#Remove Folks living Outside the USA and not American Citizens (This population was not the focus on our study and did not get treated)
alldata = alldata[alldata$Q34!="No",]
```

Splitting by assignment group for organization and easier use down the road

```{r}
controlgroupINIT = alldata[alldata$Group=='Control',]
placebogroupINIT = alldata[alldata$Group=='Placebo',]
treatmentgroupINIT = alldata[alldata$Group=='Treatment',]
```

This next chunk of code analyzes attrition overall and differentially

```{r}
#Total who did not complete study, including those who were not assigned to any group
print(as.numeric(count(alldata[alldata$Progress!="100",])))
#This includes subjects who do not meet the requirements of the study (US Resident or Citizen)

attritionc = controlgroupINIT[controlgroupINIT$Progress!="100",]
attritionp = placebogroupINIT[placebogroupINIT$Progress!="100",]
attritiont = treatmentgroupINIT[treatmentgroupINIT$Progress!="100",]

#Split by assignment group
attritc=as.numeric(count(attritionc))
attritp=as.numeric(count(attritionp))
attritt=as.numeric(count(attritiont))
attrit = attritc+attritp+attritt
```

```{r}
#Split By Assignment group and Affiliation
#Control
acr=nrow(attritionc[attritionc$Q5=='Republican',])
acd=nrow(attritionc[attritionc$Q5=='Democrat',])
aci=nrow(attritionc[attritionc$Q5=='Independent',]) + nrow(attritionc[attritionc$Q5=='Other',])

#Placebo
apr=nrow(attritionp[attritionp$Q5=='Republican',])
apd=nrow(attritionp[attritionp$Q5=='Democrat',])
api=nrow(attritionp[attritionp$Q5=='Independent',]) + nrow(attritionp[attritionp$Q5=='Other',])

#Treatment
atr=nrow(attritiont[attritiont$Q5=='Republican',])
atd=nrow(attritiont[attritiont$Q5=='Democrat',])
ati=nrow(attritiont[attritiont$Q5=='Independent',]) + nrow(attritiont[attritiont$Q5=='Other',])

```

This data is used to generate Table 2.2 from the paper.

```{r}
totalc=as.numeric(count(controlgroupINIT))
totalp=as.numeric(count(placebogroupINIT))
totalt=as.numeric(count(treatmentgroupINIT))
totalall=totalc+totalp+totalt


#Rates of attrition
#Overall
print(attrit/totalall)
#By Treatment group
print(attritc/totalc)
print(attritp/totalp)
print(attritt/totalt)


```


Chi Square Attrition Test
```{r}

attrition_tbl <- matrix(c(acr, acd, aci, apr, apd, api, atr, atd,ati), ncol=3, byrow=TRUE)
colnames(attrition_tbl) <- c('Republican', 'Democrat', 'Independent')
rownames(attrition_tbl) <- c('Contro', 'Placebo', 'Treatment')


#The null hypothesis of the independence assumption is to be rejected if the p-value of the following Chi-squared test statistics is less than a #given significance level alpha
chisq.test(attrition_tbl)

```





```{r}
compc = controlgroupINIT[controlgroupINIT$Progress=="100",]
compp = placebogroupINIT[placebogroupINIT$Progress=="100",]
compt = treatmentgroupINIT[treatmentgroupINIT$Progress=="100",]

#Split By Affiliation
#Control


ccr=print(nrow(compc[compc$Q5=='Republican',]))
ccd=print(nrow(compc[compc$Q5=='Democrat',]))
cci=print(nrow(compc[compc$Q5=='Independent',]) + nrow(compc[compc$Q5=='Other',]))

#Placebo
cpr=print(nrow(compp[compp$Q5=='Republican',]))
cpd=print(nrow(compp[compp$Q5=='Democrat',]))
cpi=print(nrow(compp[compp$Q5=='Independent',]) + nrow(compp[compp$Q5=='Other',]))

#Treatment
ctr=print(nrow(compt[compt$Q5=='Republican',]))
ctd=print(nrow(compt[compt$Q5=='Democrat',]))
cti=print(nrow(compt[compt$Q5=='Independent',]) + nrow(compt[compt$Q5=='Other',]))


comp_tbl <- matrix(c(ccr, ccd, cci, cpr, cpd, cpi, ctr, ctd,cti), ncol=3, byrow=TRUE)
colnames(comp_tbl) <- c('Republican', 'Democrat', 'Independent')
rownames(comp_tbl) <- c('Contro', 'Placebo', 'Treatment')



chisq.test(comp_tbl)

```



Figure 2.7 - Attrition plot
```{r}
attrition_gg = alldata[alldata$Progress!="100" & alldata$Group !="",]
party.lkp.df<-data.frame(response=c("Democrat","Republican", "Independent","Other"), 
                         response.no=c('Democrat','Republican',   'Other',  'Other'  ))

attrition_gg$partyplot <- party.lkp.df$response.no[match(attrition_gg$Q5, party.lkp.df$response)]
attrition_gg$partyplot <- factor(attrition_gg$partyplot, c( 'Democrat','Republican','Other'))

att_plot<-ggplot(data=attrition_gg, aes(x=Group, fill=factor(partyplot))) +
    geom_bar( position=position_stack()) + labs(x="Attrition by Treatment Group and Party") + guides(fill=guide_legend(title=NULL))+ theme( axis.text.x = element_text(colour="grey20",size=10,angle=25,hjust=.5,vjust=.5,face="plain"))  

att_plot
```

```{r}
#Remove Incomplete Surveys
alldata = alldata[alldata$Progress=="100",]
head(alldata,3)
```




```{r}
#Build Lookup Table for Question Translation
lkp.df<-data.frame(response=c('Never','Almost Never', 'Sometimes','Fairly Often', 'Very Often'),response.no=c(0,1,2,3,4))

#Create Numeric PSS Answers
alldata$PSS1 <- match(alldata$Q36, lkp.df$response)
alldata$PSS2 <- match(alldata$Q38, lkp.df$response)
alldata$PSS3 <- match(alldata$Q40, lkp.df$response)
alldata$PSS4 <- match(alldata$Q41, lkp.df$response)
alldata$PSS5 <- match(alldata$Q42, lkp.df$response)
alldata$PSS6 <- match(alldata$Q44, lkp.df$response)
alldata$PSS7 <- match(alldata$Q45, lkp.df$response)
alldata$PSS8 <- match(alldata$Q46, lkp.df$response)
alldata$PSS9 <- match(alldata$Q47, lkp.df$response)
alldata$PSS10 <- match(alldata$Q48, lkp.df$response)
alldata$PSS11 <- match(alldata$Q52, lkp.df$response)
alldata$PSS12 <- match(alldata$Q53, lkp.df$response)
alldata$PSS13 <- match(alldata$Q54, lkp.df$response)
alldata$PSS14 <- match(alldata$Q55, lkp.df$response)

#Reverse 4,5,6,7,9,10,13 based on PSS documentation
alldata$PSS4 <- 4-as.numeric(alldata$PSS4)
alldata$PSS5 <- 4-as.numeric(alldata$PSS5)
alldata$PSS6 <- 4-as.numeric(alldata$PSS6)
alldata$PSS7 <- 4-as.numeric(alldata$PSS7)
alldata$PSS9 <- 4-as.numeric(alldata$PSS9)
alldata$PSS10 <- 4-as.numeric(alldata$PSS10)
alldata$PSS13 <- 4-as.numeric(alldata$PSS13)

alldata$PSSScore <-alldata$PSS1+alldata$PSS2+alldata$PSS3+alldata$PSS4+alldata$PSS5+alldata$PSS6+alldata$PSS7+alldata$PSS8+alldata$PSS9+alldata$PSS10+alldata$PSS11+alldata$PSS12+alldata$PSS13+alldata$PSS14

alldata$PSSScore <- as.numeric(alldata$PSSScore)

```


```{r}
e <- summarize(alldata %>% group_by( alldata$Group), count=n(), ate=mean(PSSScore, na.rm=TRUE))
e
```

Refreshing dataframes for each control group for later ease

```{r}
controlgroup = alldata[alldata$Group=='Control',]
placebogroup = alldata[alldata$Group=='Placebo',]
treatmentgroup = alldata[alldata$Group=='Treatment',]
```

Looking at some simple breakdowns for party affiliation

```{r}
democrat = alldata[alldata$Q5=="Democrat",]
e <- summarize(democrat %>% group_by( democrat$Group), count=n(), ate=mean(PSSScore, na.rm=TRUE))
e
```


```{r}
republican = alldata[alldata$Q5=="Republican",]
e <- summarize(republican %>% group_by( republican$Group), count=n(), ate=mean(PSSScore, na.rm=TRUE))

e
```
```{r}
independent = alldata[alldata$Q5=="Independent",]
e <- summarize(independent %>% group_by( independent$Group), count=n(), ate=mean(PSSScore, na.rm=TRUE))

e
```

```{r}
other = alldata[alldata$Q5=="Other",]
e <- summarize(other %>% group_by( other$Group), count=n(), ate=mean(PSSScore, na.rm=TRUE))

e
```

Function to find robust standard errors

```{r}

r.se <- function(model) { 
  require(sandwich, quietly = TRUE) 
  vcov <- vcovHC(x = model, type ="HC3")
  se <- sqrt(diag(vcov))
  return(se)
}

```


Power Calculations
First we will look at control vs placebo
```{r}
ATE_P = print(mean(as.numeric(placebogroup$PSSScore), na.rm=TRUE) - mean(as.numeric(controlgroup$PSSScore), na.rm=TRUE))
combinedP = rbind(placebogroup, controlgroup)
Sigma_P = print(sd(as.numeric(combinedP$PSSScore), na.rm=TRUE))
ncountP = print(nrow(combinedP))
alpha = .05
powerval = pt(abs(ATE_P)*sqrt(ncountP)/(2*Sigma_P)-qt(1-alpha/2, df = ncountP),df = ncountP)
print(powerval)

PAS <- lm(PSSScore~Group, data=combinedP)
#PASE = summary(PAS)$coeff[2,2]
PAS$r.se <-r.se(model = PAS)
PASE = data.frame(PAS$r.se)[2,1]
placebogroup.se=PASE

placebo.ate =ATE_P


```
Same idea by political affiliation.  We do not discuss this in the paper, but we calculated power for each individual experiment by affiliation as a curiousity in case we do future work in this area.

```{r}
republicantreatment = republican[republican$Group=="Treatment",]
republicancontrol = republican[republican$Group=="Control",] 
republicanplacebo = republican[republican$Group=="Placebo",] 
democrattreatment = democrat[democrat$Group=="Treatment",]
democratcontrol = democrat[democrat$Group=="Control",] 
democratplacebo = democrat[democrat$Group=="Placebo",]
independenttreatment = independent[independent$Group=="Treatment",]
independentcontrol = independent[independent$Group=="Control",] 
independentplacebo = independent[independent$Group=="Placebo",]
othertreatment = other[other$Group=="Treatment",]
othercontrol = other[other$Group=="Control",] 
otherplacebo = other[other$Group=="Placebo",]

```

```{r}
ATE_RP = mean(as.numeric(republicanplacebo$PSSScore), na.rm=TRUE) - mean(as.numeric(republicancontrol$PSSScore), na.rm=TRUE)
combinedRP = rbind(republicanplacebo, republicancontrol)
Sigma_RP = sd(as.numeric(combinedRP$PSSScore), na.rm=TRUE)
ncountRP = nrow(combinedRP)
alpha = .05
powervalRP = pt(abs(ATE_RP)*sqrt(ncountRP)/(2*Sigma_RP)-qt(1-alpha/2, df = ncountRP),df = ncountRP)
print(powervalRP)

PRS <- lm(PSSScore~Group, data=combinedRP)
#PRSE = summary(PRS)$coeff[2,2]

PRS$r.se <-r.se(model = PRS)
PRSE = data.frame(PRS$r.se)[2,1]

```

```{r}
ATE_DP = mean(as.numeric(democratplacebo$PSSScore), na.rm=TRUE) - mean(as.numeric(democratcontrol$PSSScore), na.rm=TRUE)
combinedDP = rbind(democratplacebo, democratcontrol)
Sigma_DP = sd(as.numeric(combinedDP$PSSScore), na.rm=TRUE)
ncountDP = nrow(combinedDP)
alpha = .05
powerval = pt(abs(ATE_DP)*sqrt(ncountDP)/(2*Sigma_DP)-qt(1-alpha/2, df = ncountDP),df = ncountDP)
print(powerval)

PDS <- lm(PSSScore~Group, data=combinedDP)
#PDSE = summary(PDS)$coeff[2,2]

PDS$r.se <-r.se(model = PDS)
PDSE = data.frame(PDS$r.se)[2,1]

```

```{r}
ATE_IP = mean(as.numeric(independentplacebo$PSSScore), na.rm=TRUE) - mean(as.numeric(independentcontrol$PSSScore), na.rm=TRUE)
combinedIP = rbind(independentplacebo, independentcontrol)
Sigma_IP = sd(as.numeric(combinedIP$PSSScore), na.rm=TRUE)
ncountIP = nrow(combinedIP)
alpha = .05
powervalIP = pt(abs(ATE_IP)*sqrt(ncountIP)/(2*Sigma_IP)-qt(1-alpha/2, df = ncountIP),df = ncountIP)
print(powervalIP)

PIS <- lm(PSSScore~Group, data=combinedIP)
#PISE = summary(PIS)$coeff[2,2]

PIS$r.se <-r.se(model = PIS)
PISE = data.frame(PIS$r.se)[2,1]

```

```{r}
ATE_OP = mean(as.numeric(otherplacebo$PSSScore), na.rm=TRUE) - mean(as.numeric(othercontrol$PSSScore), na.rm=TRUE)
combinedOP = rbind(otherplacebo, othercontrol)
Sigma_OP = sd(as.numeric(combinedOP$PSSScore), na.rm=TRUE)
ncountOP = nrow(combinedOP)
alpha = .05
powervalOP = pt(abs(ATE_OP)*sqrt(ncountOP)/(2*Sigma_OP)-qt(1-alpha/2, df = ncountOP),df = ncountOP)
print(powervalOP)

POS <- lm(PSSScore~Group, data=combinedOP)
#POSE = summary(POS)$coeff[2,2]

POS$r.se <-r.se(model = POS)
POSE = data.frame(POS$r.se)[2,1]
```

Next we will look at treatment in comparison to placebo based on the same groupings as above

```{r}
ATE_T = print(mean(as.numeric(treatmentgroup$PSSScore), na.rm=TRUE) - mean(as.numeric(placebogroup$PSSScore), na.rm=TRUE))
combinedT = rbind(treatmentgroup, placebogroup)
Sigma_T = print(sd(as.numeric(combinedT$PSSScore), na.rm=TRUE))
ncountT = print(nrow(combinedT))
alpha = .05
powervalT = pt(abs(ATE_T)*sqrt(ncountT)/(2*Sigma_T)-qt(1-alpha/2, df = ncountT),df = ncountT)
print(powervalT)

TAS <- lm(PSSScore~Group, data=combinedT)
#TASE = summary(TAS)$coeff[2,2]

TAS$r.se <-r.se(model = TAS)
TASE = data.frame(TAS$r.se)[2,1]
treatmentgroup.se = TASE
treatment.ate=ATE_T
print(treatment.ate)

```

```{r}
ATE_RT = mean(as.numeric(republicantreatment$PSSScore), na.rm=TRUE) - mean(as.numeric(republicanplacebo$PSSScore), na.rm=TRUE)
combinedRT = rbind(republicantreatment, republicanplacebo)
Sigma_RT = sd(as.numeric(combinedRT$PSSScore), na.rm=TRUE)
ncountRT = nrow(combinedRT)
alpha = .05
powervalRT = pt(abs(ATE_RT)*sqrt(ncountRT)/(2*Sigma_RT)-qt(1-alpha/2, df = ncountRT),df = ncountRT)
print(powervalRT)

TRS <- lm(PSSScore~Group, data=combinedRT)
#TRSE = summary(TRS)$coeff[2,2]

TRS$r.se <-r.se(model = TRS)
TRSE = data.frame(TRS$r.se)[2,1]

```

```{r}
ATE_DT = mean(as.numeric(democrattreatment$PSSScore), na.rm=TRUE) - mean(as.numeric(democratplacebo$PSSScore), na.rm=TRUE)
combinedDT = rbind(democrattreatment, democratplacebo)
Sigma_DT = sd(as.numeric(combinedDT$PSSScore), na.rm=TRUE)
ncountDT = nrow(combinedDT)
alpha = .05
powervalDT = pt(abs(ATE_DT)*sqrt(ncountDT)/(2*Sigma_DT)-qt(1-alpha/2, df = ncountDT),df = ncountDT)
print(powervalDT)

TDS <- lm(PSSScore~Group, data=combinedDT)
#TDSE = summary(TDS)$coeff[2,2]

TDS$r.se <-r.se(model = TDS)
TDSE = data.frame(TDS$r.se)[2,1]

```



```{r}
ATE_IT = mean(as.numeric(independenttreatment$PSSScore), na.rm=TRUE) - mean(as.numeric(independentplacebo$PSSScore), na.rm=TRUE)
combinedIT = rbind(independenttreatment, independentplacebo)
Sigma_IT = sd(as.numeric(combinedIT$PSSScore), na.rm=TRUE)
ncountIT = nrow(combinedIT)
alpha = .05
powervalIT = pt(abs(ATE_IT)*sqrt(ncountIT)/(2*Sigma_IT)-qt(1-alpha/2, df = ncountIT),df = ncountIT)
print(powervalIT)

TIS <- lm(PSSScore~Group, data=combinedIT)
#TISE = summary(TIS)$coeff[2,2]


TIS$r.se <-r.se(model = TIS)
TISE = data.frame(TIS$r.se)[2,1]

```

```{r}
ATE_OT = mean(as.numeric(othertreatment$PSSScore), na.rm=TRUE) - mean(as.numeric(otherplacebo$PSSScore), na.rm=TRUE)
combinedOT = rbind(othertreatment, otherplacebo)
Sigma_OT = sd(as.numeric(combinedOT$PSSScore), na.rm=TRUE)
ncountOT = nrow(combinedOT)
alpha = .05
powervalOT = pt(abs(ATE_OT)*sqrt(ncountOT)/(2*Sigma_OT)-qt(1-alpha/2, df = ncountOT),df = ncountOT)
print(powervalOT)

TOS <- lm(PSSScore~Group, data=combinedOT)
#TOSE = summary(TOS)$coeff[2,2]


TOS$r.se <-r.se(model = TOS)
TOSE = data.frame(TOS$r.se)[2,1]

```


A dataframe collection of the above ATEs.  This data makes up table 3.1

```{r}
ATE_Data<- data.frame("Party Affiliation" = c("All", "Democrat", "Republican", "Independent","Other"), "ATE Placebo/Control" = c(ATE_P,ATE_DP,ATE_RP,ATE_IP,ATE_OP), "Standard_Error_P/C" = c(PASE,PDSE,PRSE,PISE,POSE) , "ATE Treatment/Placebo" = c(ATE_T,ATE_DT,ATE_RT,ATE_IT,ATE_OT), "Standard_Error_T/P" = c(TASE,TDSE,TRSE,TISE,TOSE) )

print(ATE_Data)

```

In stargazer form for nicer looking tables

```{r,results='asis'}
stargazer(ATE_Data,type="latex",
          summary=FALSE
)

```

Next we will look at treatment in comparison to control (as a curiousity)
```{r}
ATE_P = mean(as.numeric(treatmentgroup$PSSScore), na.rm=TRUE) - mean(as.numeric(controlgroup$PSSScore), na.rm=TRUE)
combined = rbind(treatmentgroup, controlgroup)
Sigma_P = sd(as.numeric(combined$PSSScore), na.rm=TRUE)
ncount = nrow(combined)
alpha = .05
powerval = pt(abs(ATE_P)*sqrt(ncount)/(2*Sigma_P)-qt(1-alpha/2, df = ncount),df = ncount)
print(powerval)
```

```{r}
ATE_P = mean(as.numeric(republicantreatment$PSSScore), na.rm=TRUE) - mean(as.numeric(republicancontrol$PSSScore), na.rm=TRUE)
combined = rbind(republicantreatment, republicancontrol)
Sigma_P = sd(as.numeric(combined$PSSScore), na.rm=TRUE)
ncount = nrow(combined)
alpha = .05
powerval = pt(abs(ATE_P)*sqrt(ncount)/(2*Sigma_P)-qt(1-alpha/2, df = ncount),df = ncount)
print(powerval)

```

```{r}
ATE_P = mean(as.numeric(democrattreatment$PSSScore), na.rm=TRUE) - mean(as.numeric(democratcontrol$PSSScore), na.rm=TRUE)
combined = rbind(democrattreatment, democratcontrol)
Sigma_P = sd(as.numeric(combined$PSSScore), na.rm=TRUE)
ncount = nrow(combined)
alpha = .05
powerval = pt(abs(ATE_P)*sqrt(ncount)/(2*Sigma_P)-qt(1-alpha/2, df = ncount),df = ncount)
print(powerval)
```

```{r}
ATE_P = mean(as.numeric(independenttreatment$PSSScore), na.rm=TRUE) - mean(as.numeric(independentcontrol$PSSScore), na.rm=TRUE)
combined = rbind(independenttreatment, independentcontrol)
Sigma_P = sd(as.numeric(combined$PSSScore), na.rm=TRUE)
ncount = nrow(combined)
alpha = .05
powerval = pt(abs(ATE_P)*sqrt(ncount)/(2*Sigma_P)-qt(1-alpha/2, df = ncount),df = ncount)
print(powerval)
```

Reintroduce Placebo/Treatment and Control/Placebo Data
```{r}
combinedPT = rbind(treatmentgroup, placebogroup)
combinedCP = rbind(controlgroup, placebogroup)

#And by political affiliation
republicanPT = combinedPT[combinedPT$Q5=="Republican",]
democratPT = combinedPT[combinedPT$Q5=="Democrat",]
independentPT = combinedPT[combinedPT$Q5=="Independent",]

republicanCP = combinedCP[combinedPT$Q5=="Republican",]
democratCP = combinedCP[combinedPT$Q5=="Democrat",]
independentCP = combinedCP[combinedPT$Q5=="Independent",]
```

The next sections look at various models for PSSscore vs assignment, affiliation and various other covariates.  A summary table is generated in stargazer for those chosen to be included in the paper.

```{r}
m1 <- lm(PSSScore~Group, data = combinedPT)

m1$vcovHC <- vcovHC(m1)

regsum = coeftest(m1)

print(regsum)

```

Broken Down by Political Affiliation

```{r}
#combinedPT$PSSScore

m2 <- lm(PSSScore~Group+Q5+Q5*Group, data = combinedPT)

m2$vcovHC <- vcovHC(m2)

regsum = coeftest(m2)

print(regsum)

```


Republican
```{r}
m3 <- lm(PSSScore~Group, data = republicanPT)

summary(m3)

m3$vcovHC <- vcovHC(m3)

regsum = coeftest(m3)

print(regsum)

```


Democrat
```{r}

m4 <- lm(PSSScore~Group, data = democratPT)

summary(m4)

m4$vcovHC <- vcovHC(m4)

regsum = coeftest(m4)

print(regsum)

```

Independent
```{r}

m5 <- lm(PSSScore~Group, data = independentPT)

summary(m5)

m5$vcovHC <- vcovHC(m5)

regsum = coeftest(m5)

print(regsum)

confidence_interval = get.confidence(regsum[2,1],regsum[2,2])

print(confidence_interval)

```

Looking at some other pre-treatment effects

Gender

```{r}

m6 <- lm(PSSScore~Group+Q3, data = combinedPT)

summary(m6)

m6$vcovHC <- vcovHC(m6)

regsum = coeftest(m6)

print(regsum)

confidence_interval = get.confidence(regsum[2,1],regsum[2,2])

print(confidence_interval)
```

Ethnicity

```{r}

m7 <- lm(PSSScore~Group+ethnicity, data = combinedPT)

summary(m7)

m7$vcovHC <- vcovHC(m7)

regsum = coeftest(m7)

print(regsum)

```


Age

```{r}

m8 <- lm(PSSScore~Group+as.numeric(age), data = combinedPT)

summary(m8)

m8$vcovHC <- vcovHC(m8)

regsum = coeftest(m8)

print(regsum)

confidence_interval = get.confidence(regsum[2,1],regsum[2,2])

print(confidence_interval)

```

Kitchen Sink type analysis with many covariates indluded

```{r}
m9 <- lm(PSSScore~Group+Q5*Group+Q3*Group+Q9*Group+as.numeric(age)*Group, data = combinedPT)

summary(m9)

m7$vcovHC <- vcovHC(m9)

regsum = coeftest(m9)

print(regsum)
```

Stargazer summary table for models in control/placebo experiment group.

```{r,results='asis'}
stargazer(m1,m2,m9,type="latex",
          report = "vcs*", #
          #title = "Linear Models",
          column.sep.width = "1pt",
          keep.stat = c("rsq", "n"),          
          font.size = "tiny"
          )

```

Control and Placebo experiment group with correspondign models

```{r}

m9 <- lm(PSSScore~Group, data = combinedCP)

summary(m9)

m9$vcovHC <- vcovHC(m9)

regsum = coeftest(m9)

print(regsum)

confidence_interval = get.confidence(regsum[2,1],regsum[2,2])

print(confidence_interval)

```

Broken Down by Political Affiliation

```{r}
m10 <- lm(PSSScore~Group+Q5+Q5*Group, data = combinedCP)

m10$vcovHC <- vcovHC(m10)

regsum = coeftest(m10)

print(regsum)

```

Republican
```{r}
m11 <- lm(PSSScore~Group, data = republicanCP)

summary(m11)

m11$vcovHC <- vcovHC(m11)

regsum = coeftest(m11)

print(regsum)

confidence_interval = get.confidence(regsum[2,1],regsum[2,2])

print(confidence_interval)
```

Democrat
```{r}

m12 <- lm(PSSScore~Group, data = democratCP)

summary(m12)

m12$vcovHC <- vcovHC(m12)

regsum = coeftest(m12)

print(regsum)

confidence_interval = get.confidence(regsum[2,1],regsum[2,2])

print(confidence_interval)

```

Independent
```{r}

m13 <- lm(PSSScore~Group, data = independentCP)

summary(m13)

m13$vcovHC <- vcovHC(m13)

regsum = coeftest(m13)

print(regsum)

confidence_interval = get.confidence(regsum[2,1],regsum[2,2])

print(confidence_interval)

```

Looking at some other pre-treatment effects

Gender

```{r}
m14 <- lm(PSSScore~Group+Q3, data = combinedCP)

summary(m14)

m14$vcovHC <- vcovHC(m14)

regsum = coeftest(m14)

print(regsum)

confidence_interval = get.confidence(regsum[2,1],regsum[2,2])

print(confidence_interval)
```

Ethnicity

```{r}
m15 <- lm(PSSScore~Group+ethnicity, data = combinedCP)

summary(m15)

m15$vcovHC <- vcovHC(m15)

regsum = coeftest(m15)

print(regsum)

confidence_interval = get.confidence(regsum[2,1],regsum[2,2])

print(confidence_interval)

```

Age

```{r}

m16 <- lm(PSSScore~Group+ethnicity, data = combinedCP)

summary(m16)

m16$vcovHC <- vcovHC(m16)

regsum = coeftest(m16)

print(regsum)

confidence_interval = get.confidence(regsum[2,1],regsum[2,2])

print(confidence_interval)

```

"Kitchen Sink"

```{r}
m17 <- lm(PSSScore~Group+Q5*Group+Q3*Group+Q9*Group+as.numeric(age)*Group, data = combinedCP)

summary(m17)

m17$vcovHC <- vcovHC(m17)

regsum = coeftest(m17)

print(regsum)
```

Stargazer summary table for models in placebo/treatment experiment group.

```{r,results='asis'}
stargazer(m9,m10,m17, type="latex",
          report = "vcs*", #
          #title = "Linear Models",
          column.sep.width = "1pt",
          keep.stat = c("rsq", "n"),          
          font.size = "tiny"
          #omit.table.layout = "n" # Omit more output related to errors
          )

```

This section contains various plots included in the final paper

```{r}
multiplot <- function(..., plotlist = NULL, file, cols = 1, layout = NULL) {
  require(grid)
  plots <- c(list(...), plotlist)
  numPlots = length(plots)
  if (is.null(layout)) {
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                 ncol = cols, nrow = ceiling(numPlots/cols))
}

if (numPlots == 1) {
print(plots[[1]])

} else {
grid.newpage()
pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
for (i in 1:numPlots) {
  matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
  print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                  layout.pos.col = matchidx$col))
 }
}
 }
```

Prep Data for Graphs

```{r}

all = alldata
#Make Data Values for Reports

educ2.lkp.df<-data.frame(response=c("Less than high school degree",
"High school graduate (high school diploma or equivalent including GED)", 
"Some college but no degree",
"Associate degree in college (2-year)", 
"Bachelor's degree in college (4-year)",
"Master's degree", 
"Doctoral degree",
"Professional degree (JD, MD)"), response.no=c('1. High School',
              '1. High School',
              '2. Some College',
              '2. Some College',
              '3. College',
              '4. Post College',
              '4. Post College',
              '4. Post College'
              ))

all$educplot2 <- educ2.lkp.df$response.no[match(all$Q9, educ2.lkp.df$response)]

educ.lkp.df<-data.frame(response=c("Less than high school degree",
"High school graduate (high school diploma or equivalent including GED)", 
"Some college but no degree",
"Associate degree in college (2-year)", 
"Bachelor's degree in college (4-year)",
"Master's degree", 
"Doctoral degree",
"Professional degree (JD, MD)"), response.no=c('1. High School (141)',
              '1. High School (141)',
              '2. Some College (183)',
              '2. Some College (183)',
              '3. College (197)',
              '4. Post College (130)',
              '4. Post College (130)',
              '4. Post College (130)'
              ))



all$educplot <- educ.lkp.df$response.no[match(all$Q9, educ.lkp.df$response)]


inc.lkp.df<-data.frame(response=c('Less than $10,000',
    '$10,000 to $19,999','$20,000 to $29,999','$30,000 to $39,999',
    '$40,000 to $49,999', 
    '$50,000 to $59,999',
    '$60,000 to $69,999',
    '$70,000 to $79,999',
    '$80,000 to $89,999',
    '$90,000 to $99,999',
    '$100,000 to $149,999',
    "$150,000 or more"), response.no=c( 
              'Less than $10k',
              '$10-20K',
              '$20-30K',
              '$30-40K',
              '$40-50K',
              '$50-60K',
              '$60-70K',
              '$70-80K',
              '$80-90K',
              '$90-100K',
              '$100-150K',
              '$150K or more'
              ))


all$incplot <- inc.lkp.df$response.no[match(all$Q11, inc.lkp.df$response)]
all$incplot2 <- factor(all$incplot, c('Less than $10k',
              '$10-20K',
              '$20-30K',
              '$30-40K',
              '$40-50K',
              '$50-60K',
              '$60-70K',
              '$70-80K',
              '$80-90K',
              '$90-100K',
              '$100-150K',
              '$150K or more'))

	

inc2.lkp.df<-data.frame(response=c('Less than $10,000',
    '$10,000 to $19,999','$20,000 to $29,999','$30,000 to $39,999',
    '$40,000 to $49,999', 
    '$50,000 to $59,999',
    '$60,000 to $69,999',
    '$70,000 to $79,999',
    '$80,000 to $89,999',
    '$90,000 to $99,999',
    '$100,000 to $149,999',
    "$150,000 or more"), response.no=c( 
              '$0-20K (92)',
              '$0-20K (92)',
              '$20-40K (143)',
              '$20-40K (143)',
              '$40-60K (103)',
              '$40-60K (103)',
              '$60-80K (65)',
              '$60-80K (65)',
              '$80-100K (55)',
              '$80-100K (55)',
              '$100-150K (81)',
              '$150K or more (112)'
              ))
all$inc2plot <- inc2.lkp.df$response.no[match(all$Q11, inc2.lkp.df$response)]

all$inc2plot2 <- factor(all$inc2plot, c( 
              '$0-20K (92)',
              '$20-40K (143)',
              '$40-60K (103)',
              '$60-80K (65)',
              '$80-100K (55)',
              '$100-150K (81)',
              '$150K or more (112)'))





gender.lkp.df<-data.frame(response=c("Do Not Identify (1)",
"Female (366)", 
"Male (281)",
"Transgender (3)"), response.no=c('Do not identify as female, male, or transgender',
              'Female',
              'Male',
              'Transgender'
              ))

all$genderplot <- gender.lkp.df$response[match(all$Q3, gender.lkp.df$response.no)]


all$genderplot <- factor(all$genderplot, c( 
             'Male (281)',
              'Female (366)',
               'Transgender (3)',
              'Do Not Identify (1)'
              ))




all$Q5 <- factor(all$Q5, c( 'Democrat','Republican','Independent','Other'))
all$Q4 <- factor(all$Q4, c( 'Left leaning','Republican','Central','Right leaning'))


all$incplot2 <- factor(all$incplot, c('Less than $10k',
              '$10-20K',
              '$20-30K',
              '$30-40K',
              '$40-50K',
              '$50-60K',
              '$60-70K',
              '$70-80K',
              '$80-90K',
              '$90-100K',
              '$100-150K',
              '$150K or more'))


party.lkp.df<-data.frame(response=c("Democrat",
"Republican", 
"Independent",
"Other"), response.no=c('Democrat',
              'Republican',
              'Other',
              'Other'
              ))

#all$Q5
all$partyplot <- party.lkp.df$response.no[match(all$Q5, party.lkp.df$response)]
all$partyplot <- factor(all$partyplot, c( 'Democrat','Republican','Other'))




party.lkp.df<-data.frame(response=c("Democrat",
"Republican", 
"Independent",
"Other"), response.no=c('Democrat (281)',
              'Republican (176)',
              'Other (194)',
              'Other (194)'
              ))

#all$Q5
all$partyplot2 <- party.lkp.df$response.no[match(all$Q5, party.lkp.df$response)]
all$partyplot2 <- factor(all$partyplot2, c( 'Democrat (281)','Republican (176)','Other (194)'))






age.lkp.df<-data.frame(response=c("0-20",
"21-30", 
"31-40",
"41-50",
"51-60", "Older than 60"), response.no=c('0-20 (28)',
              '21-30 (141)',
              '31-40 (137)',
              '41-50 (134)',
              '51-60 (87)',
              '60 Plus (124)'
              ))
all$ageplot <- age.lkp.df$response.no[match(all$Q1, age.lkp.df$response)]
#all$educplot <- factor(all$Q1, c( 'Democrat(281)','Republican(176)','Other(194)'))



all$PSSScore <-                as.numeric(as.character(all$PSSScore))


```

Demo Graphs - figure used in presentation
```{r}
pp1<-ggplot(data=all, aes(x=Q5, fill=factor(Group))) +
    geom_bar( position=position_dodge()) + labs(x="") +theme( axis.text.x = element_text(colour="grey20",size=10,angle=90,hjust=.5,vjust=.5,face="plain"))  + guides(fill=guide_legend(title=NULL))


pp2<-ggplot(data=all, aes(x=Q1, fill=factor(Group))) +
    geom_bar( position=position_dodge()) + labs(x="Age") + theme( axis.text.x = element_text(colour="grey20",size=10,angle=90,hjust=.5,vjust=.5,face="plain"))  + guides(fill=guide_legend(title=NULL))

pp3<-ggplot(data=all, aes(x=educplot2, fill=factor(Group))) +
    geom_bar( position=position_dodge()) + labs(x="") + theme(axis.text.x = element_text(colour="grey20",size=10,angle=90,hjust=.5,vjust=.5,face="plain")) + guides(fill=guide_legend(title=NULL))

pp4<-ggplot(data=all, aes(x=genderplot, fill=factor(Group))) +
    geom_bar( position=position_dodge()) + labs(x="") + theme(legend.text =element_text(size=8), axis.text.y = element_text(size=10) ,axis.text.x = element_text(colour="grey20",size=10,angle=90,hjust=.5,vjust=.5,face="plain"))  + guides(fill=guide_legend(title=NULL))



multiplot(pp1, pp2, pp3, pp4, cols=2)


```



Figure 2.4 - Count of treatment assignemnt groups by political affiliation, education, age, and gender

```{r}


pp1<-ggplot(data=all, aes(x=partyplot2, fill=factor(Group)))  +scale_y_continuous(breaks = c(.4, .8, 1), labels = c("40%", "80%", "100%")) +
    geom_bar( position='fill') + labs(x="", y="") + theme(axis.text.x = element_text(colour="grey20",size=10,angle=90,hjust=.5,vjust=.5,face="plain")) + guides(fill=guide_legend(title=NULL))

pp2<-ggplot(data=all, aes(x=ageplot, fill=factor(Group))) +scale_y_continuous(breaks = c(.4, .8, 1), labels = c("40%", "80%", "100%")) +
    geom_bar( position='fill') + labs(x="Age", y="") + theme( axis.text.x = element_text(colour="grey20",size=10,angle=90,hjust=.5,vjust=.5,face="plain"))  + guides(fill=guide_legend(title=NULL))



pp3<-ggplot(data=all, aes(x=educplot, fill=factor(Group)))  +scale_y_continuous(breaks = c(.4, .8, 1), labels = c("40%", "80%", "100%")) +
    geom_bar( position='fill') + labs(x="", y="") + theme(axis.text.x = element_text(colour="grey20",size=10,angle=90,hjust=.5,vjust=.5,face="plain")) + guides(fill=guide_legend(title=NULL))

pp4<-ggplot(data=all, aes(x=genderplot, fill=factor(Group)))  +scale_y_continuous(breaks = c(.4, .8, 1), labels = c("40%", "80%", "100%")) +
    geom_bar( position='fill') + labs(x="", y="") + theme(legend.text =element_text(size=8), axis.text.y = element_text(size=10) ,axis.text.x = element_text(colour="grey20",size=10,angle=90,hjust=.5,vjust=.5,face="plain"))  + guides(fill=guide_legend(title=NULL))


multiplot(pp1, pp2, cols=2)
multiplot(pp3, pp4, cols=2)

```

Figure 2.5 - Count of treatment assignment groups by income.
```{r}
ggplot(data=all, aes(x=inc2plot2, fill=factor(Group)))  +scale_y_continuous(breaks = c(.4, .8, 1), labels = c("40%", "80%", "100%")) +
    geom_bar( position='fill') + labs(x="", y="") + theme(legend.text =element_text(size=8), axis.text.y = element_text(size=10) ,axis.text.x = element_text(colour="grey20",size=10,angle=90,hjust=.5,vjust=.5,face="plain"))  + guides(fill=guide_legend(title=NULL))


```



Figure 2.6 -  Count of gender by party, political leaning by party, age by party, and political leaning by age.

```{r}
cp1<-ggplot(data=all, aes(x=partyplot, fill=factor(genderplot))) +
    geom_bar( position=position_stack()) +  labs(x="Gender by Party")  + guides(fill=guide_legend(title=NULL))+ theme( axis.text.x = element_text(colour="grey20",size=10,angle=90,hjust=.5,vjust=.5,face="plain"))  

cp2<-ggplot(data=all, aes(x=partyplot, fill=factor(Q1))) +
    geom_bar( position=position_stack()) +  labs(x="Age by Party")  + guides(fill=guide_legend(title=NULL))+ theme( axis.text.x = element_text(colour="grey20",size=10,angle=90,hjust=.5,vjust=.5,face="plain")) 

cp3<-ggplot(data=all, aes(x=partyplot, fill=factor(Q4))) +
    geom_bar( position=position_stack()) + labs(x="Political Leaning by Party") + guides(fill=guide_legend(title=NULL))+ theme( axis.text.x = element_text(colour="grey20",size=10,angle=90,hjust=.5,vjust=.5,face="plain"))  


cp4<-ggplot(data=all, aes(x=Q4, fill=factor(Q1))) +
    geom_bar( position=position_stack()) + labs(x="Political Leaning by Age ") + guides(fill=guide_legend(title=NULL))+ theme( axis.text.x = element_text(colour="grey20",size=10,angle=90,hjust=.5,vjust=.5,face="plain"))  


multiplot(cp1, cp2,cp3, cp4,cols=2)

```





Figure 3.2 - PSS Score for respondents in each of the three political affiliations
```{r}
p2 <- ggplot(data=all, aes(x=partyplot, y=PSSScore)) + 
  geom_violin(trim=FALSE)
p2 + stat_summary(fun.data="mean_sdl", mult=1, 
                 geom="pointrange", color="red") +  theme(axis.title.x=element_blank())
```

Figure 3.1 - PSS Score for the three treatment groups
```{r}
p2 <- ggplot(data=all, aes(x=Group, y=PSSScore)) + 
  geom_violin(trim=FALSE)
p2 + stat_summary(fun.data="mean_sdl", mult=1, 
                 geom="pointrange", color="red")
```

anova of age
```{r}

#mod =lm(PSSScore~Group, data = alldata)
age1 = lm(PSSScore~Group + Q1 , data = alldata)
age2 = lm(PSSScore~Group + Q1+ Q1*Group, data = alldata)

stargazer(age1, age2, type = "text")
anova(age1, age2, test = "F")




```


Figure 3.3 - Treatment Effect for the two groups.

```{r}
c= c(placebo.ate, treatment.ate)
ci.low  = c(     placebo.ate - placebogroup.se,           treatment.ate - treatmentgroup.se)
ci.high = c(     placebo.ate + placebogroup.se,           treatment.ate+ treatmentgroup.se)

p_df = cbind(c, ci.low, ci.high)
p_df = data.frame(p_df)
names(p_df) <- c("c", "low", "high")

print(p_df)
## figure 1
par(mar = c(5,7,4,2) + 0.1)
plot(x=1:2, y=p_df$c, pch = 18, ylim = c(-5,5), xlim = c(0, 3),
   xlab = "", xaxt = 'n',
   cex = 2,
   axes = FALSE, ann = FALSE,
   main = "PSS Impact from Treatment"
  )
for(i in 1:2) {
arrows(x0 = i, x1 = i, y0 = p_df$low[i], y1 = p_df$high[i], length = 0)
}
#for(i in 1:2) {
#arrows(x0 = i, x1 = i, y0 = p_df$low90[i], y1 = p_df$high90[i], length = 0, lwd = 4)
#}
abline(h=0, lty = 3, col = "black")
axis(2)
title(ylab = "PSS Reduction", line = 4.5)
title(main = "PSS Impact from Treatment")
axis(1, at = 1:2, labels = c( "Placebo", "Treatment"), tick = FALSE, cex.axis = 1)

#dev.off()

```













Figure 3.2.1 Treatment Effect by part (Placebo vs Control)
```{r}
#Graph by party for pacebo group

#c(ATE_P,ATE_DP,ATE_RP,ATE_IP,ATE_OP), "Standard_Error_P/C" = c(PASE,PDSE,PRSE,PISE,POSE) , "ATE Treatment/Placebo" = #c#(ATE_T,ATE_DT,ATE_RT,ATE_IT,ATE_OT), "Standard_Error_T/P" = c(TASE,TDSE,TRSE,TISE,TOSE) )



c= c(ATE_RP , ATE_DP, ATE_IP, ATE_OP, ATE_P)
ci.low  = c(     ATE_RP - PRSE, ATE_DP - PDSE, ATE_IP - PISE, ATE_OP - POSE ,ATE_P -PASE)
ci.high = c(     ATE_RP + PRSE, ATE_DP + PDSE, ATE_IP + PISE, ATE_OP + POSE ,ATE_P +PASE)

p_df = cbind(c, ci.low, ci.high)
p_df = data.frame(p_df)
names(p_df) <- c("c", "low", "high")

print(p_df)
## figure 1
par(mar = c(5,7,4,2) + 0.1)
plot(x=1:5, y=p_df$c, pch = 18, ylim = c(-5,10), xlim = c(1, 5),
   xlab = "", xaxt = 'n',
   cex = 2,
   axes = FALSE, ann = FALSE,
   main = "PSS Impact By Party"
  )
for(i in 1:5) {
arrows(x0 = i, x1 = i, y0 = p_df$low[i], y1 = p_df$high[i], length = 0)
}
#for(i in 1:2) {
#arrows(x0 = i, x1 = i, y0 = p_df$low90[i], y1 = p_df$high90[i], length = 0, lwd = 4)
#}
abline(h=0, lty = 3, col = "black")
axis(2)
title(ylab = "Placebo Treatment Effect on PSS Score", line = 4.5)
title(main = "Placebo vs Control PSS Impact by Party")
axis(1, at = 1:5, labels = c( "Republican", "Democrat", "Independent", "Other", "All"), tick = FALSE, cex.axis = 1)

#dev.off()



```

Figure 3.5 - Treatment vs Placebo Effect By Party
```{r}
#Graph by party for treatment group

#c(ATE_P,ATE_DP,ATE_RP,ATE_IP,ATE_OP), "Standard_Error_P/C" = c(PASE,PDSE,PRSE,PISE,POSE) , "ATE Treatment/Placebo" = #c(ATE_T,ATE_DT,ATE_RT,ATE_IT,ATE_OT), "Standard_Error_T/P" = c(TASE,TDSE,TRSE,TISE,TOSE) )



c= c(ATE_RT , ATE_DT, ATE_IT, ATE_OT, ATE_T)
ci.low  = c(     ATE_RT - TRSE, ATE_DT - TDSE, ATE_IT - TISE, ATE_OT - TOSE ,ATE_T -TASE)
ci.high = c(     ATE_RT + TRSE, ATE_DT + TDSE, ATE_IT + TISE, ATE_OT + TOSE ,ATE_T +TASE)

p_df = cbind(c, ci.low, ci.high)
p_df = data.frame(p_df)
names(p_df) <- c("c", "low", "high")

print(p_df)
## figure 1
par(mar = c(5,7,4,2) + 0.1)
plot(x=1:5, y=p_df$c, pch = 18, ylim = c(-10,5), xlim = c(1, 5),
   xlab = "", xaxt = 'n',
   cex = 2,
   axes = FALSE, ann = FALSE,
   main = "PSS Impact By Party"
  )
for(i in 1:5) {
arrows(x0 = i, x1 = i, y0 = p_df$low[i], y1 = p_df$high[i], length = 0)
}
#for(i in 1:2) {
#arrows(x0 = i, x1 = i, y0 = p_df$low90[i], y1 = p_df$high90[i], length = 0, lwd = 4)
#}
abline(h=0, lty = 3, col = "black")
axis(2)
title(ylab = "Treatment Effect on PSS Score", line = 4.5)
title(main = "Treatment vs Placebo PSS Impact by Party")
axis(1, at = 1:5, labels = c( "Republican", "Democrat", "Independent", "Other", "All"), tick = FALSE, cex.axis = 1)

#dev.off()



```










